A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-20 tex/body.tex
todo
update 1st para of chap 4

%%% TODO: Clarify that \mu-terms appear in generated models
%%% TODO: In report, give small example where Single is needed

@@

The decision procedure for (co)datatypes and its extension to quantified
formulas were presented at a high level of abstraction. This section describes
the main aspects of the implementation within the SMT solver CVC4:\ the
integration into CDCL($T$), the extension to quantified formulas, and
some optimizations.

>>>>

%%% TODO: Archive!!
%%% TODO: In report, give small example where Single is needed

@@

The ground decision procedure for (co)datatypes
was presented at a high level of abstraction. This section describes
the main aspects of the implementation within the SMT solver CVC4:\ the
integration into CDCL($T$), the extension to quantified formulas, and
some of the optimizations.
